Lens Modeling in \sw

### 2014-01-24 text/ms.tex
edits

\def\half{{\textstyle\frac12}}
% makes it easier to have consistent writing, and easy change if needed
\newcommand{\spl}{SpaghettiLens\xspace}
\newcommand{\sw}{SpaceWarps\xspace}

@@

\begin{figure}[h]
\centering
\includegraphics[width=.7\hsize]{fig/lenssky}
\caption{Sky distribution of 398 published lenses considered secure as
  of September 2013 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

% \subsection{\sw} \label{sec:SpaceWarps} some words about \sw

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6941_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6941_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6941_mass}
    \includegraphics[width=0.45\textwidth]{fig/006941_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6941_cont}
    \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6941_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6941_atime}
    \includegraphics[width=0.45\textwidth]{fig/006941_arr_time}
  }
  \caption[result 6941 (ASW000102p)]{Sim ASW000102p and a model.  A
    simple configuration; the model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6975_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6975_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6975_mass}
    \includegraphics[width=0.45\textwidth]{fig/006975_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6975_cont}
    \includegraphics[width=0.45\textwidth]{fig/006975_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6975_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006975_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6975_atime}
    \includegraphics[width=0.45\textwidth]{fig/006975_arr_time}
  }
  \caption[result 6975 (ASW000195x)]{Sim ASW000195x and a
    model.}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6937_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6937_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6937_mass}
    \includegraphics[width=0.45\textwidth]{fig/006937_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6937_cont}
    \includegraphics[width=0.45\textwidth]{fig/006937_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6937_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006937_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6937_atime}
    \includegraphics[width=0.45\textwidth]{fig/006937_arr_time}
  }
  \caption[result 6937 (ASW0000vqg)]{Sim ASW0000vqg and a model.}
  \label{fig:6937}
\end{figure}

@@

  \caption[result 6990 (ASW0004oux)]{Sim ASW0004oux and a model.}
  \label{fig:6990}
\end{figure}

@@

  \caption[result 6915 (ASW0001hpf)]{Sim ASW0001hpf and a model. Inclined quad.}
  \label{fig:6915}
\end{figure}

@@

  \caption[result 7022 (ASW0000h2m)]{Sim ASW0000h2m and a model.  The
    model input appears in the middle panel of Figure
    \ref{fig:input-spag}.}
  \label{fig:7022}
\end{figure}

@@

  \caption[result 7025 (ASW0000h2m)]{Sim ASW0000h2m and another model.  The image parities in this case were incorrectly identified.}
  \label{fig:7025}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6919_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6919_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6919_mass}
    \includegraphics[width=0.45\textwidth]{fig/006919_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6919_cont}
    \includegraphics[width=0.45\textwidth]{fig/006919_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6919_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006919_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6919_atime}
    \includegraphics[width=0.45\textwidth]{fig/006919_arr_time}
  }
  \caption[result 6919 (ASW0002z6f)]{Sim ASW0002z6f and a model.  The
    model input appears in the bottom panel of Figure
    \ref{fig:input-spag}. An incipient quad}
  \label{fig:6919}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007020_kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007024_kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc for models of \asw{0h2m} with incorrect image identifications. \figref{7022} shows a model (by an expert) with the correct identifications, while \figref{7025} shows a model with error E06 (parities rotated by $\pi/2$).  Shown here are the \kenc results for two models with error E06 and one model (bottom) with error E05 (parities rotated by $\pi$).}
\label{fig:kapenc_compare_faulty}
\end{figure}

@@

>>>>

\def\half{{\textstyle\frac12}}
% makes it easier to have consistent writing, and easy change if needed
\newcommand{\spl}{SpaghettiLens\xspace}
\newcommand{\sw}{Spacewarps\xspace}

@@

\begin{figure}[h]
\centering
\includegraphics[width=.7\hsize]{fig/lenssky}
\caption{Sky distribution of 423 published lenses considered secure as
  of January 2014 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6941_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6941_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6941_mass}
    \includegraphics[width=0.45\textwidth]{fig/006941_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6941_cont}
    \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6941_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6941_atime}
    \includegraphics[width=0.45\textwidth]{fig/006941_arr_time}
  }
  \caption[result 6941 (ASW000102p)]{Model results for a simple
    simulated lens.  (The label ASW000102p in the lower-left panel is
    the \sw identifier for the sky patch where this sim was placed.)
    The model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6975_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6975_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6975_mass}
    \includegraphics[width=0.45\textwidth]{fig/006975_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6975_cont}
    \includegraphics[width=0.45\textwidth]{fig/006975_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6975_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006975_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6975_atime}
    \includegraphics[width=0.45\textwidth]{fig/006975_arr_time}
  }
  \caption[result 6975 (ASW000195x)]{A model for a sim with some mass
    substructure. (See Section \ref{sec:example_models} for details.)}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6937_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6937_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6937_mass}
    \includegraphics[width=0.45\textwidth]{fig/006937_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6937_cont}
    \includegraphics[width=0.45\textwidth]{fig/006937_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6937_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006937_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6937_atime}
    \includegraphics[width=0.45\textwidth]{fig/006937_arr_time}
  }
  \caption[result 6937 (ASW0000vqg)]{A sim with substructure,
    resulting in a poor mass model. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:6937}
\end{figure}

@@

  \caption[result 6990 (ASW0004oux)]{Model of a four-image
    system. (See Section \ref{sec:example_models} for details.)}
  \label{fig:6990}
\end{figure}

@@

  \caption[result 6915 (ASW0001hpf)]{Model of another four-image
    system. (See Section \ref{sec:example_models} for details.)}
  \label{fig:6915}
\end{figure}

@@

  \caption[result 7022 (ASW0000h2m)]{A further four-image system. The
    model input appears in the middle panel of Figure
    \ref{fig:input-spag}. (See Section \ref{sec:example_models} for
    details.)}
  \label{fig:7022}
\end{figure}

@@

  \caption[result 7025 (ASW0000h2m)]{Another model for the lens
    appearing in \figref{fig:7022}.  The image parities in this case
    were incorrectly identified, resulting in a rather poor model, but
    the estimated Einstein radius is not bad. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:7025}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6919_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6919_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6919_mass}
    \includegraphics[width=0.45\textwidth]{fig/006919_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6919_cont}
    \includegraphics[width=0.45\textwidth]{fig/006919_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6919_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006919_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6919_atime}
    \includegraphics[width=0.45\textwidth]{fig/006919_arr_time}
  }
  \caption[result 6919 (ASW0002z6f)]{A sim on the border case of
    double vs quad; modelled as a quad.  The model input appears in
    the bottom panel of Figure \ref{fig:input-spag}. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:6919}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007020_kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007024_kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc from three models of a system with incorrect image identifications. \figref{7022} shows a model (by an expert) with the correct identifications, while \figref{7025} shows a model with error E06 (parities rotated by $\pi/2$).  Shown here are the \kenc results for two models with error E06 and one model (bottom) with error E05 (parities rotated by $\pi$).}
\label{fig:kapenc_compare_faulty}
\end{figure}

@@

\section{Acknowledgments}

We thank the Swiss Society for Astrophysics and Astronomy and the
Swiss Academy of Sciences.
